Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-09 Detailed_analyses_for_paper.Rmd
renamed rmd file (since these aren't really the figures for the manuscript)

  # update feed production CO2 (with error)
   scenarios[which(scenarios$Variable == "feed_prod_CO2"),coln][1:2]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])*
                           c(1-feed_prod_error,1+feed_prod_error)

  # update feed transport CO2 (with error)
   scenarios[which(scenarios$Variable == "feed_trans_CO2"),coln][1:2]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])*
                           c(1-feed_trans_error,1+feed_trans_error)

@@

precise_inputs<-read.csv(input_table)[,c(1:7)] 
precise_vars<-precise_inputs[which(!is.na(precise_inputs$IPCC_default)),]

@@

  # update feed production CO2 (with error)
   precise_scenarios[which(precise_scenarios$Variable == "feed_prod_CO2"),coln]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])

  # update feed transport CO2 (with error)
   precise_scenarios[which(precise_scenarios$Variable == "feed_trans_CO2"),coln]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])

@@

*# THIS STILL NEEDS CHECKING - are all the units correct?*

@@

ggsave("Fig_14_no_bulls_scatter_per_head_milk_emissions_intensity.png",width=9,height=9)

@@

@@

```{r, include=FALSE}
breed_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(breed_res_endline,"results","Breed_intervention_endline")
```

```{r, include=FALSE}
adoption_rate <- 1
breed_res_endline<-load_temperature_scenarios("results","Breed_intervention_endline")
class(breed_res_endline)<-"mcSimulation"
```

@@

ggsave("Fig_19_breed_endline.png", width=9,height=9)

@@

ggsave("Fig_20_breed_endline_errors.png", width=5,height=5)

@@

```{r, include=FALSE, eval=FALSE}
nobull_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(nobull_res_endline,"results","Nobull_intervention_endline")
```

```{r, include=FALSE}
adoption_rate <- 1
nobull_res_endline<-load_temperature_scenarios("results","Nobull_intervention_endline")
class(nobull_res_endline)<-"mcSimulation"
```

@@

ggsave("Fig_21_nobull_endline.png", width=9,height=9)

@@

ggsave("Fig_22_nobull_endline_errors.png", width=5,height=5)

@@

```{r, include=FALSE, eval=FALSE}
lessReplace_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(lessReplace_res_endline,"results","lessReplace_intervention_endline")
```

```{r, include=FALSE}
lessReplace_res_endline<-load_temperature_scenarios("results","lessReplace_intervention_endline")
class(lessReplace_res_endline)<-"mcSimulation"
```

@@

ggsave("Fig_23_lessReplace_endline.png", width=9,height=9)

@@

ggsave("Fig_24_lessReplace_endline_errors.png", width=5,height=5)

@@

plot_pls(pls_out,input_table=legend_table)
ggsave("Fig_25_PLS_dairy_households.png", width=8,height=5)
```

@@

- Feed intervention (how exactly?)
- Select what to present in the manuscript and the supplement

>>>>

  # update feed production CO2 (with error)
   scenarios[which(scenarios$Variable == "feed_prod_CO2"),coln][1:2]<-
     sum(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])*
                           c(1-feed_prod_error,1+feed_prod_error)

  # update feed transport CO2 (with error)
   scenarios[which(scenarios$Variable == "feed_trans_CO2"),coln][1:2]<-
     sum(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])*
                           c(1-feed_trans_error,1+feed_trans_error)

@@

precise_inputs<-read.csv(input_table)[,c(1:8)] 
precise_vars<-precise_inputs[which(!is.na(precise_inputs$IPCC_default)),]

@@

  # update feed production CO2 (with error)
   precise_scenarios[which(precise_scenarios$Variable == "feed_prod_CO2"),coln]<-
     sum(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])

  # update feed transport CO2 (with error)
   precise_scenarios[which(precise_scenarios$Variable == "feed_trans_CO2"),coln]<-
     sum(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])

@@

@@

ggsave("Fig_14_nobull_scatter_per_head_milk_emissions_intensity.png",width=9,height=9)

@@

# Feed intervention 1 - Supplementary legume fodder

Animal feeds are supplemented with cuttings from the legumious tree Calliandra. This expected to have the following impacts:

- milk yield of non-dry cows (i.e. animal types 5 and 6) rises by 0.156 kg per day
- the digestible energy (DE) of the diet rises by 0.14 percentage points
- the crude protein content of the diet (CP) drops by 0.07 percentage points
- feed emissions drop by 0.726 kg CO2 per animal and year

We assume that 30% of households adopt this intervention.

```{r}
x_Calliandra_intervention <- GHG_simulation_scenarios$x

Calliandra_adoption_rate <- 0.3

for (i in 1:nrow(x_Calliandra_intervention))
{
  if (rbinom(1, 1, Calliandra_adoption_rate)) # if farmers adopt, make changes in x file
    {x_Calliandra_intervention$milk_yield_5[i]<-x_Calliandra_intervention$milk_yield_5[i]+0.156
     x_Calliandra_intervention$milk_yield_6[i]<-x_Calliandra_intervention$milk_yield_6[i]+0.156
     x_Calliandra_intervention$DE_perc[i]<-x_Calliandra_intervention$DE_perc[i]+0.14
     x_Calliandra_intervention$perc_crude_protein_diet[i]<-x_Calliandra_intervention$perc_crude_protein_diet[i]-0.07
     x_Calliandra_intervention$feed_prod_CO2[i]<-x_Calliandra_intervention$feed_prod_CO2[i]- (0.726 *
                                        sum(x_Calliandra_intervention[i,paste0("N_animal_type_",1:12)]))

  }
}
# run model for modified x file
Calliandra_res <- run_model(x_Calliandra_intervention, ghg_emissions)

```{r, include=FALSE}
Calliandra_res$call<-"multi-scenario call"
save_temperature_scenarios(Calliandra_res,"results","Calliandra_intervention")
```

```{r, include=FALSE}
Calliandra_res<-load_temperature_scenarios("results","Calliandra_intervention")
class(Calliandra_res)<-"mcSimulation"
```

## Emissions intensity response to introducing legume fodder

Calliandra_res$y[,"CO2eq_per_milk"]<-Calliandra_res$y$pc_on_farm/Calliandra_res$y$pc_milk_yield

Calliandra_res$y<-Calliandra_res$y[normal_milk_yield,]
Calliandra_res$x<-Calliandra_res$x[normal_milk_yield,]

impact_of_Calliandra<-data.frame(baseline=dairy_households$y$pc_milk_yield,
                                  Calliandra_milk=Calliandra_res$y$pc_milk_yield,
                                  CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,
                                  CO2_intensity_Calliandra=Calliandra_res$y$CO2eq_per_milk)
impact_of_Calliandra[,"milk_change"]<-
  round(impact_of_Calliandra$Calliandra_milk-impact_of_Calliandra$baseline,2)
impact_of_Calliandra[,"emissions_intensity_change"]<-
  round(impact_of_Calliandra$CO2_intensity_Calliandra-impact_of_Calliandra$CO2_intensity_baseline ,3)

lessRep_scatter<-ggplot(data=impact_of_Calliandra,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point() +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emission~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per capita milk yield (kg)")

lessRep_probs<-ggplot(data = decreased_emissions_probability,
                      aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_Calliandra[which(impact_of_Calliandra$milk_change>0),],
             aes(x=baseline,y=Calliandra_milk)) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~of~'higher-productivity'~farm~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~'lower-productivity'~farm~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") + theme_bw()

ggsave("Fig_19_Calliandra_reductions.png", width=9,height=9)

Still need to define something adequate for the next section.

Calliandra_diagnosis<-Calliandra_res
Calliandra_diagnosis$y[,"baseline_pc_milk_yield"]<-dairy_households$y$pc_milk_yield

for(i in 1:nrow(Calliandra_diagnosis$x))
  {decreased_emissions_probability[,"diff"]<-
    abs(decreased_emissions_probability$Base_yield-Calliandra_diagnosis$y$baseline_pc_milk_yield[i]) +
    abs(decreased_emissions_probability$new_yield-Calliandra_diagnosis$y$pc_milk_yield[i])
  Calliandra_diagnosis$y[i,"confidence_level"]<-decreased_emissions_probability$probability[which(decreased_emissions_probability$diff==min(decreased_emissions_probability$diff))][1]
}

Calliandra_90_farms<-Calliandra_diagnosis$x$Scenario[which(Calliandra_diagnosis$y$confidence_level>0.9)]

Calliandra_diagnosis$x["Farm"]<-sapply(Calliandra_diagnosis$x$Scenario,
                                  function(x) as.numeric(strsplit(x,"_")[[1]][2]))

Calliandra_structures<-merge(Calliandra_diagnosis$x,farm_structures)
Calliandra_structures<-list(x=Calliandra_structures, y=Calliandra_diagnosis$y)

to_plot<-cbind(Farm=Calliandra_structures$x$Farm,Confidence_level=Calliandra_structures$y$confidence_level,
               Calliandra_structures$x[,c(paste0("breed_",1:8),"unproductive_bulls","replacement_males")])
to_plot$other_animals<-1-to_plot$replacement_males

ggsave("Fig_20_Calliandra_diagnostics.png",width=5,height=5)

**This needs change - sensitive factors not analyzed so far**

# Feed intervention 2 - Balanced diets

- milk yield per cow rises by 0.75 kg per day
- feed emissions drop by 328.5 kg CO2 per animal and year

We assume that 14% of farms adopt this intervention.

```{r}
x_balance_intervention <- GHG_simulation_scenarios$x

balance_adoption_rate <- 0.14

for (i in 1:nrow(x_balance_intervention))
{
  if (rbinom(1, 1, balance_adoption_rate)) # if farmers adopt, make changes in x file
    {x_balance_intervention$milk_yield_5[i]<-x_balance_intervention$milk_yield_5[i]+0.75
     x_balance_intervention$milk_yield_6[i]<-x_balance_intervention$milk_yield_6[i]+0.75
     x_balance_intervention$feed_prod_CO2[i]<-x_balance_intervention$feed_prod_CO2[i]-(328.5 * 
                    sum(x_Calliandra_intervention[i,paste0("N_animal_type_",1:12)]))
  }
}
# run model for modified x file
balance_res <- run_model(x_balance_intervention, ghg_emissions)

```{r, include=FALSE}
balance_res$call<-"multi-scenario call"
save_temperature_scenarios(balance_res,"results","balance_intervention")
```

```{r, include=FALSE}
balance_res<-load_temperature_scenarios("results","balance_intervention")
class(balance_res)<-"mcSimulation"
```

## Emissions intensity response to introduction of balanced diets

balance_res$y[,"CO2eq_per_milk"]<-balance_res$y$pc_on_farm/balance_res$y$pc_milk_yield

balance_res$y<-balance_res$y[normal_milk_yield,]
balance_res$x<-balance_res$x[normal_milk_yield,]

impact_of_balance<-data.frame(baseline=dairy_households$y$pc_milk_yield,
                                  balance_milk=balance_res$y$pc_milk_yield,
                                  CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,
                                  CO2_intensity_balance=balance_res$y$CO2eq_per_milk)
impact_of_balance[,"milk_change"]<-
  round(impact_of_balance$balance_milk-impact_of_balance$baseline,2)
impact_of_balance[,"emissions_intensity_change"]<-
  round(impact_of_balance$CO2_intensity_balance-impact_of_balance$CO2_intensity_baseline ,3)

balance_scatter<-ggplot(data=impact_of_balance,
                        aes(x=milk_change,y=emissions_intensity_change)) +
  geom_point() +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emission~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per capita milk yield (kg)")

balance_probs<-ggplot(data = decreased_emissions_probability,
                      aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_balance[which(impact_of_balance$milk_change>0),],
             aes(x=baseline,y=balance_milk)) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~of~'higher-productivity'~farm~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~'lower-productivity'~farm~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") + theme_bw()

balance_scatter + balance_probs +
  plot_layout(ncol = 1, nrow = 2)

ggsave("Fig_21_balance_reductions.png", width=9,height=9)

Still need to define something adequate for the next section.

balance_diagnosis<-balance_res
balance_diagnosis$y[,"baseline_pc_milk_yield"]<-dairy_households$y$pc_milk_yield

for(i in 1:nrow(balance_diagnosis$x))
  {decreased_emissions_probability[,"diff"]<-
    abs(decreased_emissions_probability$Base_yield-balance_diagnosis$y$baseline_pc_milk_yield[i]) +
    abs(decreased_emissions_probability$new_yield-balance_diagnosis$y$pc_milk_yield[i])
  balance_diagnosis$y[i,"confidence_level"]<-decreased_emissions_probability$probability[which(decreased_emissions_probability$diff==min(decreased_emissions_probability$diff))][1]
}

balance_90_farms<-balance_diagnosis$x$Scenario[which(balance_diagnosis$y$confidence_level>0.9)]

balance_diagnosis$x["Farm"]<-sapply(balance_diagnosis$x$Scenario,
                                  function(x) as.numeric(strsplit(x,"_")[[1]][2]))

balance_structures<-merge(balance_diagnosis$x,farm_structures)
balance_structures<-list(x=balance_structures, y=balance_diagnosis$y)

to_plot<-cbind(Farm=balance_structures$x$Farm,Confidence_level=balance_structures$y$confidence_level,
               balance_structures$x[,c(paste0("breed_",1:8),"unproductive_bulls","replacement_males")])
to_plot$other_animals<-1-to_plot$replacement_males

ggsave("Fig_22_balance_diagnostics.png",width=5,height=5)

**This needs change - sensitive factors not analyzed so far**

@@

```{r, include=FALSE}
breed_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(breed_res_endline,"results","End_Breed_intervention")
```

```{r, include=FALSE}
adoption_rate <- 1
breed_res_endline<-load_temperature_scenarios("results","End_Breed_intervention")
class(breed_res_endline)<-"mcSimulation"
```

@@

ggsave("Fig_23_breed_endline.png", width=9,height=9)

@@

ggsave("Fig_24_breed_endline_errors.png", width=5,height=5)

@@

```{r, include=FALSE, eval=FALSE}
nobull_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(nobull_res_endline,"results","End_nobull_intervention")
```

```{r, include=FALSE}
adoption_rate <- 1
nobull_res_endline<-load_temperature_scenarios("results","End_nobull_intervention")
class(nobull_res_endline)<-"mcSimulation"
```

@@

ggsave("Fig_25_nobull_endline.png", width=9,height=9)

@@

ggsave("Fig_26_nobull_endline_errors.png", width=5,height=5)

@@

```{r, include=FALSE, eval=FALSE}
lessReplace_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(lessReplace_res_endline,"results","End_lessReplace_intervention")
```

```{r, include=FALSE}
lessReplace_res_endline<-load_temperature_scenarios("results","End_lessReplace_intervention")
class(lessReplace_res_endline)<-"mcSimulation"
```

@@

ggsave("Fig_27_lessReplace_endline.png", width=9,height=9)

@@

ggsave("Fig_28_lessReplace_endline_errors.png", width=5,height=5)

## Feed intervention 1 - Supplementary legume fodder

We can do the same analysis for supplementing cow nutrition with Calliandra.

# Calliandra intervention
Calliandra_adopters<-which(!x_Calliandra_intervention$DE_perc==GHG_simulation_scenarios$x$DE_perc)

x_Calliandra_intervention_endline <- GHG_simulation_scenarios_time2$x

x_Calliandra_intervention_endline$N_animal_type_3[Calliandra_adopters]<-0

x_Calliandra_intervention$milk_yield_5[Calliandra_adopters]<-x_Calliandra_intervention$milk_yield_5[Calliandra_adopters]+0.156
x_Calliandra_intervention$milk_yield_6[Calliandra_adopters]<-x_Calliandra_intervention$milk_yield_6[Calliandra_adopters]+0.156
x_Calliandra_intervention$DE_perc[Calliandra_adopters]<-x_Calliandra_intervention$DE_perc[Calliandra_adopters]+0.14
x_Calliandra_intervention$perc_crude_protein_diet[Calliandra_adopters]<-x_Calliandra_intervention$perc_crude_protein_diet[Calliandra_adopters]-0.07
x_Calliandra_intervention$feed_prod_CO2[Calliandra_adopters]<-x_Calliandra_intervention$feed_prod_CO2[Calliandra_adopters]- (0.726 *
                                  sum(x_Calliandra_intervention[Calliandra_adopters,paste0("N_animal_type_",1:12)]))

# run model for modified x file
Calliandra_res_endline <- run_model(x_Calliandra_intervention_endline, ghg_emissions)

```{r, include=FALSE, eval=FALSE}
Calliandra_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(Calliandra_res_endline,"results","End_Calliandra_intervention")
```

```{r, include=FALSE}
Calliandra_res_endline<-load_temperature_scenarios("results","End_Calliandra_intervention")
class(Calliandra_res_endline)<-"mcSimulation"
```

```{r, fig.dim = c(8, 8)}
Calliandra_res_endline$y$Calliandra_adopters<-NA
Calliandra_res_endline$y$Calliandra_adopters[Calliandra_adopters]<-"Adopter"
Calliandra_res_endline$y$Calliandra_adopters[is.na(Calliandra_res_endline$y$Calliandra_adopters)]<-"Non-adopter"

Calliandra_res_endline$y[,"CO2eq_per_milk"]<-Calliandra_res_endline$y$pc_on_farm/Calliandra_res_endline$y$pc_milk_yield

Calliandra_res_endline$y<-Calliandra_res_endline$y[normal_milk_yield,]
Calliandra_res_endline$x<-Calliandra_res_endline$x[normal_milk_yield,]

impact_of_Calliandra_endline<-data.frame(baseline=dairy_households$y$pc_milk_yield,
                                  Calliandra_endline_milk=Calliandra_res_endline$y$pc_milk_yield,
                                  CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,
                                  CO2_intensity_Calliandra=Calliandra_res_endline$y$CO2eq_per_milk,
                                  Adopter=Calliandra_res_endline$y$Calliandra_adopters)
impact_of_Calliandra_endline[,"milk_change"]<-
  round(impact_of_Calliandra_endline$Calliandra_endline_milk-impact_of_Calliandra_endline$baseline,2)
impact_of_Calliandra_endline[,"emissions_intensity_change"]<-
  round(impact_of_Calliandra_endline$CO2_intensity_Calliandra-impact_of_Calliandra_endline$CO2_intensity_baseline ,3)

Calliandra_endline_scatter<-ggplot(data=impact_of_Calliandra_endline,
                        aes(x=milk_change,y=emissions_intensity_change,color=Adopter)) +
  geom_point(size=0.5) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emission~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per capita milk yield (kg)") + scale_color_manual(values=c("Adopter" = "darkslategrey", "Non-adopter" = "burlywood"))

Calliandra_endline_probs<-ggplot(data = decreased_emissions_probability,
                      aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_Calliandra_endline[which(impact_of_Calliandra_endline$milk_change>0),],
             aes(x=baseline,y=Calliandra_endline_milk,color=Adopter), size=0.5) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~of~'higher-productivity'~farm~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~'lower-productivity'~farm~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") + theme_bw() + scale_color_manual(values=c("Adopter" = "darkslategrey", "Non-adopter" = "burlywood"))

Calliandra_endline_scatter + Calliandra_endline_probs +
  plot_layout(ncol = 1, nrow = 2)

ggsave("Fig_29_Calliandra_endline.png", width=9,height=9)

```{r}
Calliandra_endline_diagnosis<-Calliandra_res_endline
Calliandra_endline_diagnosis$y[,"baseline_pc_milk_yield"]<-dairy_households$y$pc_milk_yield

for(i in 1:nrow(Calliandra_endline_diagnosis$x))
  {decreased_emissions_probability[,"diff"]<-
    abs(decreased_emissions_probability$Base_yield-Calliandra_endline_diagnosis$y$baseline_pc_milk_yield[i]) +
    abs(decreased_emissions_probability$new_yield-Calliandra_endline_diagnosis$y$pc_milk_yield[i])
  Calliandra_endline_diagnosis$y[i,"confidence_level"]<-decreased_emissions_probability$probability[which(decreased_emissions_probability$diff==min(decreased_emissions_probability$diff))][1]
}

confidence_level_analysis_Calliandra<-data.frame(confidence=seq(0.5,1,0.01))
n_adopt<-length(which(Calliandra_endline_diagnosis$y$Calliandra_adopter=="Adopter"))
n_nonadopt<-length(which(Calliandra_endline_diagnosis$y$Calliandra_adopter=="Non-adopter"))
for(i in 1:nrow(confidence_level_analysis_Calliandra))
{confidence_level_analysis_Calliandra$Type1error[i]<-length(which(Calliandra_endline_diagnosis$y$Calliandra_adopter=="Adopter" &
                                                 Calliandra_endline_diagnosis$y$confidence_level<confidence_level_analysis_Calliandra$confidence[i])) / n_adopt * 100
 confidence_level_analysis_Calliandra$Type2error[i]<-length(which(Calliandra_endline_diagnosis$y$Calliandra_adopter=="Non-adopter" &
                                                 Calliandra_endline_diagnosis$y$confidence_level>confidence_level_analysis_Calliandra$confidence[i])) / n_nonadopt * 100

}
confidence_level_analysis_Calliandra$confidence<-confidence_level_analysis_Calliandra$confidence*100

toplot<-melt(confidence_level_analysis_Calliandra,id.vars = "confidence")
toplot$variable <- factor(toplot$variable, levels = c("Type1error", "Type2error"),
                  labels = c("Type I error - failure to reward adopters", "Type II error - rewarding non-adopters"))

ggsave("Fig_30_Calliandra_endline_errors.png", width=5,height=5)

## Feed intervention 2 - Balanced diets

We can do the same analysis for a balanced diet.

# balance intervention
balance_adopters<-which(!x_balance_intervention$feed_prod_CO2==GHG_simulation_scenarios$x$feed_prod_CO2)

x_balance_intervention_endline <- GHG_simulation_scenarios_time2$x

x_balance_intervention$milk_yield_5[balance_adopters]<-x_balance_intervention$milk_yield_5[balance_adopters]+0.75
x_balance_intervention$milk_yield_6[balance_adopters]<-x_balance_intervention$milk_yield_6[balance_adopters]+0.75
x_balance_intervention$feed_prod_CO2[balance_adopters]<-x_balance_intervention$feed_prod_CO2[balance_adopters]-(328.5 * 
                    sum(x_Calliandra_intervention[balance_adopters,paste0("N_animal_type_",1:12)]))

# run model for modified x file
balance_res_endline <- run_model(x_balance_intervention_endline, ghg_emissions)

```{r, include=FALSE, eval=FALSE}
balance_res_endline$call<-"multi-scenario call"
save_temperature_scenarios(balance_res_endline,"results","End_balance_intervention")
```

```{r, include=FALSE}
balance_res_endline<-load_temperature_scenarios("results","End_balance_intervention")
class(balance_res_endline)<-"mcSimulation"
```

```{r, fig.dim = c(8, 8)}
balance_res_endline$y$balance_adopters<-NA
balance_res_endline$y$balance_adopters[balance_adopters]<-"Adopter"
balance_res_endline$y$balance_adopters[is.na(balance_res_endline$y$balance_adopters)]<-"Non-adopter"

balance_res_endline$y[,"CO2eq_per_milk"]<-balance_res_endline$y$pc_on_farm/balance_res_endline$y$pc_milk_yield

balance_res_endline$y<-balance_res_endline$y[normal_milk_yield,]
balance_res_endline$x<-balance_res_endline$x[normal_milk_yield,]

impact_of_balance_endline<-data.frame(baseline=dairy_households$y$pc_milk_yield,
                                  balance_endline_milk=balance_res_endline$y$pc_milk_yield,
                                  CO2_intensity_baseline= dairy_households$y$CO2eq_per_milk,
                                  CO2_intensity_balance=balance_res_endline$y$CO2eq_per_milk,
                                  Adopter=balance_res_endline$y$balance_adopters)
impact_of_balance_endline[,"milk_change"]<-
  round(impact_of_balance_endline$balance_endline_milk-impact_of_balance_endline$baseline,2)
impact_of_balance_endline[,"emissions_intensity_change"]<-
  round(impact_of_balance_endline$CO2_intensity_balance-impact_of_balance_endline$CO2_intensity_baseline ,3)

balance_endline_scatter<-ggplot(data=impact_of_balance_endline,
                        aes(x=milk_change,y=emissions_intensity_change,color=Adopter)) +
  geom_point(size=0.5) +
  theme_bw() +
  ggtitle("Intervention impact on milk yield and emissions") + 
  labs(y=expression(Change~'in'~emission~intensity~(kg~CO[2]*'-eq'~kg^-1)),
       x="Change in per capita milk yield (kg)") + scale_color_manual(values=c("Adopter" = "darkslategrey", "Non-adopter" = "burlywood"))

balance_endline_probs<-ggplot(data = decreased_emissions_probability,
                      aes(Base_yield, new_yield)) +
  geom_contour_filled(aes(z=probability)) +
  stat_contour(breaks = c(0.9),aes(z=probability),col="black") +
  geom_point(data=impact_of_balance_endline[which(impact_of_balance_endline$milk_change>0),],
             aes(x=baseline,y=balance_endline_milk,color=Adopter), size=0.5) +
  ggtitle("Probability of lower emissions intensity on higher-productivity farm") + 
  labs(y=expression(Milk~yield~of~'higher-productivity'~farm~(kg~head^{-1}~year^{-1})),
       x=expression(Milk~yield~of~'lower-productivity'~farm~(kg~head^{-1}~year^{-1})),
       fill="Probability of \nlower emissions \nintensity") + theme_bw() + scale_color_manual(values=c("Adopter" = "darkslategrey", "Non-adopter" = "burlywood"))

balance_endline_scatter + balance_endline_probs +
  plot_layout(ncol = 1, nrow = 2)

ggsave("Fig_31_balance_endline.png", width=9,height=9)

```{r}
balance_endline_diagnosis<-balance_res_endline
balance_endline_diagnosis$y[,"baseline_pc_milk_yield"]<-dairy_households$y$pc_milk_yield

for(i in 1:nrow(balance_endline_diagnosis$x))
  {decreased_emissions_probability[,"diff"]<-
    abs(decreased_emissions_probability$Base_yield-balance_endline_diagnosis$y$baseline_pc_milk_yield[i]) +
    abs(decreased_emissions_probability$new_yield-balance_endline_diagnosis$y$pc_milk_yield[i])
  balance_endline_diagnosis$y[i,"confidence_level"]<-decreased_emissions_probability$probability[which(decreased_emissions_probability$diff==min(decreased_emissions_probability$diff))][1]
}

confidence_level_analysis_balance<-data.frame(confidence=seq(0.5,1,0.01))
n_adopt<-length(which(balance_endline_diagnosis$y$balance_adopter=="Adopter"))
n_nonadopt<-length(which(balance_endline_diagnosis$y$balance_adopter=="Non-adopter"))
for(i in 1:nrow(confidence_level_analysis_balance))
{confidence_level_analysis_balance$Type1error[i]<-length(which(balance_endline_diagnosis$y$balance_adopter=="Adopter" &
                                                 balance_endline_diagnosis$y$confidence_level<confidence_level_analysis_balance$confidence[i])) / n_adopt * 100
 confidence_level_analysis_balance$Type2error[i]<-length(which(balance_endline_diagnosis$y$balance_adopter=="Non-adopter" &
                                                 balance_endline_diagnosis$y$confidence_level>confidence_level_analysis_balance$confidence[i])) / n_nonadopt * 100

}
confidence_level_analysis_balance$confidence<-confidence_level_analysis_balance$confidence*100

toplot<-melt(confidence_level_analysis_balance,id.vars = "confidence")
toplot$variable <- factor(toplot$variable, levels = c("Type1error", "Type2error"),
                  labels = c("Type I error - failure to reward adopters", "Type II error - rewarding non-adopters"))

ggsave("Fig_32_balance_endline_errors.png", width=5,height=5)

@@

plot_pls(pls_out,input_table=legend_table)
ggsave("Fig_33_PLS_dairy_households.png", width=8,height=5)
```

@@

- Select what to present in the manuscript and the supplement
